\documentclass{article}
\usepackage[utf8]{inputenc}

\title{wk 9 submission}
\author{Thomas Kongonis}
\date{October 2019}

\begin{document}

\maketitle

\section{Opening Comments}
\begin{itemize}
\item{Due to other graded assessments i did not manage to complete the expected workload for this submission. That being said i will just outline the work that i have done up until now.}
\end{itemize}

\section{changes to user stories}

\begin{itemize}
    \item{After beginning to complete the steps that i needed to, i came across some new user stories and the project had a few additions.}
    
    \item{\textbf{User Story 1:} As a student, i want to be able to view multiple  translations alongside each other, so that i don’t have to go searching every time i get confused with a translated term.}
    \item{\textbf{User Story 2:} As a student i should be able to find public domain translations.}
    \item{\textbf{User Story 3:} As a student, i should be able to use the Shell Command in lieu of a GUI.}
    \item{\textbf{User Story 4:} As a student, i should be able to write a shell script that will accurately title each chapter of selected translations.}
    \item{\textbf{User Story 5:} As a student, i should be able to write a shell script that can pull up a specific chapter of 4 translations within the shell command.}
    
\end{itemize}

\section{Other Work}
\begin{itemize}
\item{\textbf{Gathering Translations:} I encountered some difficulty gathering translations but i managed to find 4 in the public domain that i could transfer to .txt format without too much difficulty.}
\item{Alongside this, i experimented with.xml and had too many difficulties, therefore i decided that i would utilise a wildcard shell script to pull the chapters up.}
\item{My two options for the translations is to write a Shell script that will label each chapter in 5 separate translation files, or i could write a script that will take each chapter and turn it into a separate file and put it into a directory relevant to the translation.}
\end{itemize}

\begin{itemize}
    \item{To conclude, this is all i had time to complete this week and i thought it would be better to submit this rather than nothing.}
\end{itemize}
\end{document}
